Optimal Peak Shaving With Storage Battery and Bifacial Solar PV

### 2023-12-19 Paper/tex/paper.tex
working mdpi format and bibtex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{geometry}

\author{}
\date{}

@@

\hypertarget{abstract}{%
  \section{Abstract}\label{abstract}}

Electric load peak shaving is a challenging and important problem
considering the rapid growth of high power electric vehicle charging
sites. Co-located solar photovoltaic provides locally produced energy,
but an additional storage battery is required for reliable peak shaving.
With occasional evening load peaks and an electric tariff with a
16:00-21:00 peak time of use period, vertical bifacial modules facing
West have an economic advantage due to more of the production shifted
into the late afternoon and early evening. Exploiting this, an optimal
electric load peak shaving simulator dispatches a stationary battery to
minimize the retail electric cost incurred by a real electric vehicle
charging site over 10 months. Five different case studies of co-located
bifacial solar photovoltaic arrays are simulated, a base case oriented
South and tilted at 20° and four experimental cases where a percentage
(25\%, 50\%, 75\%, or 100\%) of the array is oriented West and tilted at
90°. The problem is formulated such that the optimizer minimizes the
retail electric cost by adjusting three peak power thresholds, each
corresponding to a time of use period with an associated power price in
\(\$/kW\). The optimizer is implemented using a Newton-Raphson gradient
descent approach and the optimality of the method is verified to within
0.1 \(kW\). A sensitivity analysis on battery energy capacity results in
a largest cost reduction, relative to the South 20° base case, of \$1422
(6.7\%) achieved by the 50\% West 90° case and a modest 25 kWh battery.
A second sensitivity analysis on solar power capacity shows that the
cost reduction increases monotonically and logarithmically for all cases
and battery capacities. The largest cost decrease is \$2579 (16.1\%),
achieved by the 75\% West 90° case at 200\% of nominal solar capacity
along with a 125 kWh battery. Both data and code are shared to the
public on GitHub.

\hypertarget{introduction}{%
  \section{Introduction}\label{introduction}}

\hypertarget{why-peak-load}{%
  \subsection{Why peak load}\label{why-peak-load}}

@@

\hypertarget{peak-shaving}{%
  \subsection{Peak shaving}\label{peak-shaving}}

@@

\hypertarget{technical}{%
  \subsubsection{Technical}\label{technical}}

@@

\hypertarget{economic}{%
  \subsubsection{Economic}\label{economic}}

@@

\hypertarget{methodology}{%
  \section{Methodology}\label{methodology}}

\begin{figure}
  \centering
  \includegraphics[width=5cm,height=\textheight]{./images/oneline.png}
  \caption{Charging Site One Line Schematic. Simplified
  one-line schematic of the simulated EV charging station with true
  measured EV charging power, modelled on-site solar generation, and a
  modelled stationary battery for economic peak shaving.}
  \label{fig:oneline}
\end{figure}

@@

\hypertarget{data}{%
  \subsection{Data}\label{data}}

\hypertarget{ev-charging-load}{%
  \subsubsection{\texorpdfstring{EV Charging Load
    }{EV Charging Load }}\label{ev-charging-load}}

@@

\hypertarget{solar-production}{%
  \subsubsection{Solar Production}\label{solar-production}}

@@

\begin{table}[!h]
  \centering
  \caption{Timeseries Data Summary. EV charging power is
  measured every 10 seconds for 10 months at the Jet Propulsion
  Laboratory, CA, USA. Solar irradiance from the GOES satellite is
  acquired for the same location. Solar PV array production is modelled
  from the satellite irradiance using a 6 parameter PV cell model and
  inverter efficiency lookup table.\label{tab:loadsectors}}
  \label{tab:data-summary}
  \begin{tabularx}{\textwidth}{XXXXX}
  \toprule
  Timeseries Description & Location & Type & Interval / Length & Source  \\
  \midrule
  \vtop{\hbox{\strut EV charging power}\hbox{\strut (\(kW_{ac}\))}} & Jet
  Propulsion Lab, Pasadena CA, USA                                  & Measured and aggregated from multiple
  EV chargers at single site                                        & 10 sec (average downsampled to 15 min) / 10
  months                                                            & Caltech ACN \\

  \vtop{\hbox{\strut Solar irradiance }\hbox{\strut (\(W/m^2\))}}   & GPS:
  34.2013, -118.1721 (2x2 km square)                                & GOES satellite irradiance                                 & 5
  minute / 10 months                                                & NSRDB PSMv3 \\

  PV array production (\(kW_{ac}\))                                 & GPS: 34.2013, -118.1721 (2x2 km
  square)                                                           & Modelled from satellite irradiance, 368 Prism Solar 350 W
  bifacial modules, 368 Enphase IQH 380 W microinverters            & 15 minute / 10
  months                                                            & SAM (Gilman 2015) \\

@@

\hypertarget{battery}{%
  \subsection{Battery}\label{battery}}

@@

\hypertarget{electric-tariff}{%
  \subsection{Electric Tariff}\label{electric-tariff}}

@@

\begin{table}[!h]
  \centering
  \caption{Retail Electric Tariff. An applicable electric
  tariff schedule with seven different TOU periods for energy and power
  prices, varying by hours of the day and season of the year. From
  California PG\&E.}
  \label{tab:tariff}
  \begin{tabularx}{\textwidth}{XXXXX}
  \toprule
  Name                                   & TOU Period                                               & Summer (Jun 1 - Sept 30) {[}\${]}                   & Winter (Oct 1 -Feb 28) {[}\${]}   & Spring (Mar 1 - May 30) {[}\${]}  \\
  \midrule
  All hours                              & 0:00-0:00                                                & 26.07 / kW                                          & 26.07 / kW      & 26.07 / kW \\
  Super off-peak                         & 9:00-14:00                                               & -\/-                                                & -\/-            & 0.079 / kWh \\
  Off-peak spring                        & \vtop{\hbox{\strut 0:00-9:00,14:00-16:00,}\hbox{\strut 21:00-0:00}} & -\/-                                                     & -\/-              & 0.132 / kWh \\
  Off-peak winter                        & 0:00-16:00, 21:00-0:00                                   & -\/-                                                & 0.132 / kWh     & -\/-\\
  Off-peak summer                        & 0:00-14:00, 23:00-0:00                                   & 0.132 / kWh                                         & -\/-            & -\/-\\
  Partial-peak                           & 14:00-16:00, 21:00-23:00                                 & \vtop{\hbox{\strut 6.81 /
  kW,}\hbox{\strut 0.159 / kWh}}         & -\/-                                                     & -\/-\\
  Peak                                   & 16:00-21:00                                              & \vtop{\hbox{\strut 32.90 / kW,}\hbox{\strut 0.196 /
  kWh}}                                  & \vtop{\hbox{\strut 2.22 / kW,}\hbox{\strut 0.172 / kWh}} & \vtop{\hbox{\strut 2.22 / kW}\hbox{\strut ,0.172 / kWh}}\\

  Consequence of exceeding the threshold & Damage to infrastructure,possible outage & Monetary cost depending on tariff \\
  \bottomrule
  \end{tabularx}
\end{table}

@@

\hypertarget{peak-shaving-algorithm}{%
  \subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}}

@@

\begin{figure}
  \centering
  \includegraphics[width=10cm,height=\textheight]{./images/peak shaving flowchart.png}
  \caption{Peak Shaving Flowchart. Net load is the
  timeseries of load less solar. There is one threshold value for one for
  each TOU period with a non-zero power price. For each timestep of the
  simulation the net load is compared to the threshold of that TOU period,
  and the battery is discharged if the net load is greater than the
  threshold and charged if the net load is less than the threshold. If the
  two are equal the battery does nothing. For timesteps with no price on
  power the the battery does nothing.}
  \label{fig:peakshaving-flowchart}
\end{figure}

@@

\hypertarget{threshold-optimizer}{%
  \subsection{Threshold Optimizer}\label{threshold-optimizer}}

@@

\hypertarget{simulations}{%
  \subsection{Simulations}\label{simulations}}

@@

\begin{figure}
  \centering
  \includegraphics[width=15cm,height=\textheight]{./images/simulation flowchart.png}
  \caption{Simulation Flowchart. Given a solar orientation
  and chosen battery capacity, the net load timeseries is calculated from
  EV charging load and solar production. The threshold optimizer produces
  one threshold value (kW) for each TOU period with non-zero power prices.
  This returns both optimal thresholds and a minimum cost. Lastly a 1
  month simulation of the battery charging and discharging is performed to
  ensure no violations of the battery technical limits, and to produce the
  battery power timeseries for evaluation.}
  \label{fig:simulation-flowchart}
\end{figure}

\hypertarget{case-studies}{%
  \section{Case Studies}\label{case-studies}}

@@

\begin{table}
  \centering
  \caption{Case Studies. All modules are the Prism 350 W
  bifacial. The base case is South-facing array tilted to 20°. In the
  following four cases a percentage of the modules are oriented such that
  the primary high power module surface faces West and the modules are
  tilted to 90°: 25\%, 50\%, 75\%, and 100\%. As an increasing portion of
  the array is oriented West and vertical the total energy and solar yield
  decrease linearly as expected.}
  \label{tab:casestudies}
  \begin{tabularx}{\textwidth}{XXXXXX}
  \toprule
  Case Study                                   & No. Modules                               & Orientation & Tilt & \vtop{\hbox{\strut Total Energy }\hbox{\strut {[}\(MWh\){]}}}         & \vtop{\hbox{\strut Solar Yield}\hbox{\strut  {[}\(\frac{kWh}{kW_{DC}}\){]}}}\\
  \midrule
  South 20°                                    & 368                                       & South       & 20°  & 151.7                    & 1180.8\\
  25\% West 90°                                & \vtop{\hbox{\strut 276}\hbox{\strut 92}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 146.5                                     & 1140.4\\
  50\% West 90°                                & \vtop{\hbox{\strut 184}\hbox{\strut 184}} & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 141.1                                     & 1098.2\\
  75\% West 90°                                & \vtop{\hbox{\strut 92}\hbox{\strut 276}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 136.1                                     & 1059.6\\
  100\% West 90°                               & 368                                       & West        & 90°  & 131.0                    & 1019.3\\
  \bottomrule
  \end{tabularx}
\end{table}

\hypertarget{results}{%
  \section{Results}\label{results}}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost.png}
  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost reduction.png}
  \caption{Total Cost. Total Retail Electric Cost is calculated for each
  solar array case study and a sensitivity analysis is performed on
  battery capacity (kWh). Below 150 kW the South 20° and 100\% West 90°
  arrays have similarly high total costs, whereas the three combination
  arrays are somewhat grouped a few percent below. Above 150 kW the total
  costs for each case diverge somewhat, with the South 20° base case
  attaining the lowest cost for the 400 kWh battery and larger.
  RIGHT: Reduction in Total Retail Cost is likely the most important metric for
  evaluating the peak shaving efficacy, since it can be directly used as
  revenue in a cash flow analysis to calculate economic performance. The
  combination 50\% West 90° array with 100 kWh battery achieve the largest
  cost reduction of \$1422 (6.7\%) over the 10 month data period. A
  selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
  \label{fig:total-cost}
\end{figure}

>>>>

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

\usepackage[acronym]{glossaries}
\usepackage{hhline}
\usepackage{threeparttable} % to use table notes
%\usepackage[draft]{changes} % usage: \deleted{old} \added{new} \replaced{new}{old} also \hl{} for highlighted text
%\usepackage[final]{changes}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Optimal Peak Shaving With Storage Battery and Bifacial Solar PV}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Optimal Peak Shaving With Storage Battery and Bifacial Solar PV}

\newcommand{\orcidauthorA}{0000-0003-0237-4148} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-2106-0374} % Add \orcidB{} behind the author's name

\newcommand{\orcidauthorC}{0000-0002-7883-0034}

% Authors, for the paper (add full first names)
\Author{
  Michael Wood $^{1,2,*}$\orcidA{},
  Emanuele Ogliari $^{1}$\orcidB{},
  Travis Simpkins $^{2}$, and
  Sonia Leva $^{1}$\orcidC{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Michael Wood, Emanuele Ogliari, Travis Simpkins, and Sonia Leva}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Wood, M.; Ogliari, E.; Simpkins, T.; Leva, S.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Energy, Politecnico di Milano, Via Lambruschini 4a, 20156, Milan, Italy; emanuelegiovanni.ogliari@polimi.it (E.O.); sonia.leva@polimi.it (S.L.) \\
$^{2}$ \quad muGrid Analyics LLC., 14143 Denver West Parkway Ste 100, Golden, CO, USA; travis@mugrid.com}

% Contact information of the corresponding author
\corres{Correspondence: michael.wood@polimi.it}

\abstract{Electric load peak shaving is a challenging and important problem
considering the rapid growth of high power electric vehicle charging
sites. Co-located solar photovoltaic provides locally produced energy,
but an additional storage battery is required for reliable peak shaving.
With occasional evening load peaks and an electric tariff with a
16:00-21:00 peak time of use period, vertical bifacial modules facing
West have an economic advantage due to more of the production shifted
into the late afternoon and early evening. Exploiting this, an optimal
electric load peak shaving simulator dispatches a stationary battery to
minimize the retail electric cost incurred by a real electric vehicle
charging site over 10 months. Five different case studies of co-located
bifacial solar photovoltaic arrays are simulated, a base case oriented
South and tilted at 20° and four experimental cases where a percentage
(25\%, 50\%, 75\%, or 100\%) of the array is oriented West and tilted at
90°. The problem is formulated such that the optimizer minimizes the
retail electric cost by adjusting three peak power thresholds, each
corresponding to a time of use period with an associated power price in
\(\$/kW\). The optimizer is implemented using a Newton-Raphson gradient
descent approach and the optimality of the method is verified to within
0.1 \(kW\). A sensitivity analysis on battery energy capacity results in
a largest cost reduction, relative to the South 20° base case, of \$1422
(6.7\%) achieved by the 50\% West 90° case and a modest 25 kWh battery.
A second sensitivity analysis on solar power capacity shows that the
cost reduction increases monotonically and logarithmically for all cases
and battery capacities. The largest cost decrease is \$2579 (16.1\%),
achieved by the 75\% West 90° case at 200\% of nominal solar capacity
along with a 125 kWh battery. Both data and code are shared to the
public on GitHub.}

% Keywords
\keyword{electric load; peak shaving; bifacial solar PV; EV charging;}

@@

\section{Introduction}\label{introduction}

\subsection{Why peak load}\label{why-peak-load}

@@

%\hypertarget{peak-shaving}{%
\subsection{Peak shaving}\label{peak-shaving}%}

@@

%\hypertarget{technical}{%
\subsubsection{Technical}\label{technical}%}

@@

%\hypertarget{economic}{%
\subsubsection{Economic}\label{economic}%}

@@

%\hypertarget{methodology}{%
\section{Methodology}\label{methodology}%}

\begin{figure}
  \centering
  \includegraphics[width=7.5cm]{./images/oneline.png}
  \caption{Charging Site One Line Schematic. Simplified
  one-line schematic of the simulated EV charging station with true
  measured EV charging power, modelled on-site solar generation, and a
  modelled stationary battery for economic peak shaving.}
  \label{fig:oneline}
\end{figure}

@@

%\hypertarget{data}{%
\subsection{Data}\label{data}%}

%\hypertarget{ev-charging-load}{%
%\subsubsection{\texorpdfstring{EV Charging Load
%    }{EV Charging Load }}\label{ev-charging-load}%}
\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}

@@

%\hypertarget{solar-production}{%
\subsubsection{Solar Production}\label{solar-production}%}

@@

\begin{table}[!h]
  \centering
  \caption{Timeseries Data Summary. EV charging power is
  measured every 10 seconds for 10 months at the Jet Propulsion
  Laboratory, CA, USA. Solar irradiance from the GOES satellite is
  acquired for the same location. Solar PV array production is modelled
  from the satellite irradiance using a 6 parameter PV cell model and
  inverter efficiency lookup table.\label{tab:loadsectors}}
  \label{tab:data-summary}
  \begin{tabularx}{\linewidth}{XXXXX}
    % { >{\hsize=.25\hsize\linewidth=\hsize}X
    %   >{\hsize=.25\hsize\linewidth=\hsize}X
    %   >{\hsize=.7\hsize\linewidth=\hsize}X
    %   >{\hsize=.1\hsize\linewidth=\hsize}X
    %   >{\hsize=.2\hsize\linewidth=\hsize}X
    % }
  %\begin{tabularx}{llllll}
  \toprule
  Description & Location & Type & Interval & Source  \\
  \midrule
  EV charging power ($kW_{ac}$) & Jet Propulsion Lab, Pasadena CA, USA & Measured and aggregated from multiple  EV chargers at single site & 10 sec (average downsampled to 15 min) & Caltech ACN \\
  Solar irradiance ($W/m^2$)   & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance & 5 min & NSRDB PSMv3 \\
  PV array production ($kW_{ac}$) & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min & SAM (Gilman 2015) \\

@@

%\hypertarget{battery}{%
\subsection{Battery}\label{battery}%}

@@

%\hypertarget{electric-tariff}{%
\subsection{Electric Tariff}\label{electric-tariff}%}

@@

\begin{table}[!h]
  \centering
  \caption{Retail Electric Tariff. An applicable electric
  tariff schedule with seven different TOU periods for energy and power
  prices, varying by hours of the day and season of the year. From
  California PG\&E.}
  \label{tab:tariff}
  \begin{tabularx}{\textwidth}{XXXXX}
  \toprule
  Name                                   & TOU Period                                               & Summer (Jun 1 - Sept 30) $[\$]$                   & Winter (Oct 1 -Feb 28) $[\$]$   & Spring (Mar 1 - May 30) $[\$]$  \\
  \midrule
  All hours                              & 0:00-0:00                                                & 26.07/$kW$                                          & 26.07/$kW$                        & 26.07/$kW$ \\
  Super off-peak                         & 9:00-14:00                                               & -\/-                                                & -\/-                              & 0.079/$kWh$ \\
  Off-peak spring                        & 0:00-9:00, 14:00-16:00, 21:00-0:00                       & -\/-                                                & -\/-                              & 0.132/$kWh$ \\
  Off-peak winter                        & 0:00-16:00, 21:00-0:00                                   & -\/-                                                & 0.132/$kWh$                       & -\/-\\
  Off-peak summer                        & 0:00-14:00, 23:00-0:00                                   & 0.132/$kWh$                                         & -\/-                              & -\/-\\
  Partial-peak                           & 14:00-16:00, 21:00-23:00                                 & 6.81/$kW$, 0.159/$kWh$                              & -\/-                              & -\/-\\
  Peak                                   & 16:00-21:00                                              & 32.90/$kW$, 0.196/$kWh$                             & 2.22/$kW$, 0.172/$kWh$            & 2.22/$kW$, 0.172/$kWh$    \\
  \bottomrule
  \end{tabularx}
\end{table}

@@

%\hypertarget{peak-shaving-algorithm}{%
\subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}%}

@@

\begin{figure}
  \centering
  \includegraphics[width=7.5cm]{./images/peak shaving flowchart.png}
  \caption{Peak Shaving Flowchart. Net load is the
  timeseries of load less solar. There is one threshold value for one for
  each TOU period with a non-zero power price. For each timestep of the
  simulation the net load is compared to the threshold of that TOU period,
  and the battery is discharged if the net load is greater than the
  threshold and charged if the net load is less than the threshold. If the
  two are equal the battery does nothing. For timesteps with no price on
  power the the battery does nothing.}
  \label{fig:peakshaving-flowchart}
\end{figure}

@@

%\hypertarget{threshold-optimizer}{%
\subsection{Threshold Optimizer}\label{threshold-optimizer}%}

@@

%\hypertarget{simulations}{%
\subsection{Simulations}\label{simulations}%}

@@

\begin{figure}
  \centering
  \includegraphics[width=12cm]{./images/simulation flowchart.png}
  \caption{Simulation Flowchart. Given a solar orientation
  and chosen battery capacity, the net load timeseries is calculated from
  EV charging load and solar production. The threshold optimizer produces
  one threshold value (kW) for each TOU period with non-zero power prices.
  This returns both optimal thresholds and a minimum cost. Lastly a 1
  month simulation of the battery charging and discharging is performed to
  ensure no violations of the battery technical limits, and to produce the
  battery power timeseries for evaluation.}
  \label{fig:simulation-flowchart}
\end{figure}

%\hypertarget{case-studies}{%
\section{Case Studies}\label{case-studies}%}

@@

\begin{table}
  \centering
  \caption{Case Studies. All modules are the Prism 350 W
  bifacial. The base case is South-facing array tilted to 20°. In the
  following four cases a percentage of the modules are oriented such that
  the primary high power module surface faces West and the modules are
  tilted to 90°: 25\%, 50\%, 75\%, and 100\%. As an increasing portion of
  the array is oriented West and vertical the total energy and solar yield
  decrease linearly as expected.}
  \label{tab:casestudies}
  \begin{tabularx}{\textwidth}{XXXXXX}
  \toprule
  Case Study                      & Modules     & Orientation & Tilt  & Total Energy ($MWh$)        & Solar Yield ($\frac{kWh}{kW_{DC}}$) \\
  \midrule
  South 20°                       & 368         & South       & 20°   & 151.7                       & 1180.8\\
  \hline
  \multirow{2}{*}{25\% West 90°}  & 276         & South       & 20°   &\multirow{2}{*}{146.5}       & \multirow{2}{*}{1140.4}\\
                                  & 92          & West        & 90°   &                             &                         \\
  \hline
  \multirow{2}{*}{50\% West 90°}  & 184         & South       & 20°   & \multirow{2}{*}{141.1}      & \multirow{2}{*}{1098.2}\\
                                  & 184         & West        & 90°   &                             & \\                              
  \hline                                  
  \multirow{2}{*}{75\% West 90°}  & 92          & South       & 20°   & \multirow{2}{*}{136.1}      & \multirow{2}{*}{1059.6}\\
                                  & 276         & West        & 90°   &                             & \\                       
  \hline
  100\% West 90°                  & 368         & West        & 90°   & 131.0                       & 1019.3 \\                                                                              
  \bottomrule
  \end{tabularx}
\end{table}

%\hypertarget{results}{%
\section{Results}\label{results}%}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=6.8cm]{./images/total cost.png}
  \includegraphics[width=6.8cm]{./images/total cost reduction.png}
  \caption{Total Cost. Total Retail Electric Cost is calculated for each
  solar array case study and a sensitivity analysis is performed on
  battery capacity (kWh). Below 150 kW the South 20° and 100\% West 90°
  arrays have similarly high total costs, whereas the three combination
  arrays are somewhat grouped a few percent below. Above 150 kW the total
  costs for each case diverge somewhat, with the South 20° base case
  attaining the lowest cost for the 400 kWh battery and larger.
  RIGHT: Reduction in Total Retail Cost is likely the most important metric for
  evaluating the peak shaving efficacy, since it can be directly used as
  revenue in a cash flow analysis to calculate economic performance. The
  combination 50\% West 90° array with 100 kWh battery achieve the largest
  cost reduction of \$1422 (6.7\%) over the 10 month data period. A
  selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
  \label{fig:total-cost}
\end{figure}
